---
title: "Improving the accuracy of a regression model"
output: github_document
---

[article](https://towardsdatascience.com/how-to-improve-the-accuracy-of-a-regression-model-3517accf8604)

```{r include = F}
# loading required libraries
library(tidyverse) # necessary functions
library(patchwork) # patch together visualisations
library(ggcorrplot) # create correlation heatmap
library(GGally) # for pairwise plots
library(caret) # MAE and RMSE functions

# setting some quality of life options
knitr::opts_chunk$set(message = F, warning = F, fig.align = "center")
options(scipen = 999)
theme_set(theme_minimal())
```

```{r}
# importing the data
df = read_csv("https://raw.githubusercontent.com/sacharya225/data-expts/master/Health%20Insurance%20Cost%20Prediction/insurance.csv",
         col_types = cols())
```

```{r}
# finding the dimensions of the data
paste0(nrow(df), " rows; ", ncol(df), " columns")
```

```{r}
# checking if/where we have NA values
colSums(is.na(df))
```

```{r}
# using the median to impute NA values
df = df |>
  mutate(age = ifelse(is.na(age), median(df$age, na.rm = T), age),
         bmi = ifelse(is.na(bmi), median(df$bmi, na.rm = T), bmi))

# confirming we imputed where the NA values were
colSums(is.na(df))
```

```{r message = F}
# pairwise plots for numeric variables using GGally
df |>
  dplyr::select(where(is.numeric)) |>
  ggpairs()
```

```{r}
# creating plots for categorical variables
sex_counts_plot = df |>
  count(sex) |>
  ggplot(aes(sex, n)) +
  geom_col(aes(fill = sex)) +
  scale_fill_manual(values = c("#FAD7FF", "#CEE4FC")) +
  theme_classic() +
  labs(x = NULL, y = NULL,
       title = "gender counts") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 2.5))
  

smoker_counts_plot = df |>
  count(smoker) |>
  ggplot(aes(smoker, n)) +
  geom_col(aes(fill = smoker)) +
  scale_fill_manual(values = c("#FFC2B9", "#BEDFC1")) +
  theme_classic() +
  labs(x = NULL, y = NULL,
       title = "smoker counts") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 2.5))

children_counts_plot = df |>
  count(children) |>
  mutate(children = factor(children)) |>
  ggplot(aes(children, n)) +
  geom_col(aes(fill = children), alpha = 0.5) +
  theme_classic() +
  labs(x = NULL, y = NULL,
       title = "children counts") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 2.5))

region_counts_plot = df |>
  count(region) |>
  ggplot(aes(region, n)) +
  geom_col(aes(fill = region), alpha = 0.5) +
  theme_classic() +
  labs(x = NULL, y = NULL,
       title = "region counts") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, vjust = 2.5))
```

```{r}
# combining plots into one with patchwork package
sex_counts_plot + smoker_counts_plot + children_counts_plot + region_counts_plot
```

```{r}
# visualising distribution of charges among categorical variable values
charges_sex_plot = df |>
  ggplot(aes(sex, charges)) +
  geom_boxplot(aes(fill = sex), outlier.alpha = 0.25, outlier.shape = 4) +
  scale_fill_manual(values = c("#FAD7FF", "#CEE4FC")) +
  labs(x = NULL, y = NULL,
       title = "charges v. sex") +
  theme_classic() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))

charges_smoker_plot = df |>
  ggplot(aes(smoker, charges)) +
  geom_boxplot(aes(fill = smoker), outlier.alpha = 0.25, outlier.shape = 4) +
  scale_fill_manual(values = c("#FFC2B9", "#BEDFC1")) +
  labs(x = NULL, y = NULL,
       title = "charges v. smoker") +
  theme_classic() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))

charges_children_plot = df |>
  mutate(children = factor(children)) |>
  ggplot(aes(children, charges)) +
  geom_boxplot(aes(fill = children), outlier.alpha = 0.25, outlier.shape = 4, alpha = 0.5) +
  labs(x = NULL, y = NULL,
       title = "charges v. children") +
  theme_classic() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))

charges_region_plot = df |>
  ggplot(aes(region, charges)) +
  geom_boxplot(aes(fill = region), outlier.alpha = 0.25, outlier.shape = 4, alpha = 0.5) +
  labs(x = NULL, y = NULL,
       title = "charges v. region") +
  theme_classic() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))
```

```{r}
# combining previous plots with patchwork
charges_sex_plot + charges_smoker_plot + charges_children_plot + charges_region_plot
```

```{r}
# making more plots showing distribution of charges for smoker and children
charges_smoker_density = df |>
  ggplot(aes(charges)) +
  geom_density(aes(fill = smoker), col = "transparent", alpha = 0.8) +
  scale_fill_manual(values = c("#BEDFC1", "#FFC2B9")) +
  theme_classic() +
  labs(title = "density curves of charges v. smoker") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_blank())

charges_children_density = df |>
  ggplot(aes(charges)) +
  geom_density(aes(fill = factor(children)), col = "transparent", alpha = 0.25) +
  theme_classic() +
  labs(title = "density curves of charges v. children",
       fill = "children") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_blank())
```

```{r}
# putting density curve plots together with patchwork
charges_smoker_density / charges_children_density
```

```{r}
# additional visual of charges among values of children
charges_prop_plot = df |>
  mutate(children = factor(children)) |>
  group_by(children) |>
  summarise(charges = sum(charges),
            n = n()) |>
  mutate(prop = round(n / sum(n), 3),
         charges_prop = round(charges / sum(charges), 3)) |>
  select(children, prop, charges_prop) |>
  pivot_longer(!children, names_to = "prop_type", values_to = "value") |>
  mutate(prop_type = ifelse(prop_type == "prop", "observations", "charges")) |>
  ggplot(aes(children, value)) +
  geom_col(aes(fill = prop_type), position = "dodge") +
  geom_text(aes(label = value, group = prop_type), position = position_dodge(width = 1), vjust = -0.5, size = 3) +
  scale_fill_manual(values = c("#BEDFC1", "#D2BEDF")) +
  labs(fill = "proportion type",
       title = "charges are higher for observations with 2, 3, or 4 children") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_blank())

charges_prop_plot
```

```{r}
# building a correlation heatmap with ggcorrplot package
df |>
  select(where(is.numeric)) |>
  cor() |>
  ggcorrplot(type = "lower",
             outline.color = "black",
             legend.title = "correlation",
             title = "correlation plot of numeric variables",
             colors = c("indianred3", "white", "springgreen4"),
             lab = T,
             hc.order = T) +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
# visualising distribution of sex among all smokers
df |>
  filter(smoker == "yes") |>
  count(sex) |>
  ggplot(aes(sex, n)) +
  geom_col(aes(fill = sex)) +
  scale_fill_manual(values = c("#FFD2FE", "#C7DBFF")) +
  geom_text(aes(label = n), vjust = -0.5, size = 3.5) +
  theme_classic() +
  labs(x = NULL, y = "count",
       title = "among smokers, there are more males than females") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_blank())
```


___

a few observations:

- males & females are roughly equal when it comes to median charges, but the range of values is larger for males
- charges appear to be significantly higher for smokers
- charges appear to be highest for people with 2 or 3 children
- customers are roughly equally distribution among the four regions and charges appear to be roughly the same among the four
- among smokers in the data, we have 159 males compared to 115 females

___

### Preparation for modeling

```{r}
# converting variables to factors
df = df |>
  mutate(sex = factor(sex),
         children = factor(children),
         smoker = factor(smoker),
         region = factor(region))
```

Note that despite taking numeric values, `children` has been converted to a factor because it is not truly a continuous variable.

```{r}
model_formula = charges ~ .
lmMod = lm(model_formula, data = df)

relImportance = relaimpo::calc.relimp(lmMod, type = "lmg",  rela = F)

# relative importances
sort(round(relImportance$lmg, 3), decreasing = T)
```

I will now perform a series of ANOVA tests to see what the best predictor variables will be for our model.

```{r}
# experimenting with different models based on feature importance
mod1 = lm(charges ~ smoker, data = df)
mod2 = lm(charges ~ smoker + age, data = df)

anova(mod1, mod2)
```

This tells us the model with both `smoker` and `age` as predictors is better than the model with only `smoker` as a predictor.

```{r}
mod1 = lm(charges ~ smoker + age, data = df)
mod2 = lm(charges ~ smoker + age + bmi, data = df)

anova(mod1, mod2)
```

This tells us our model is also improved when we add `bmi` as a predictor.

```{r}
mod1 = lm(charges ~ smoker + age + bmi, data = df)
mod2 = lm(charges ~ smoker + age + bmi + children, data = df)

anova(mod1, mod2)
```

This tells us our model is better when we include `children` as a predictor.

```{r}
mod1 = lm(charges ~ smoker + age + bmi + children, data = df)
mod2 = lm(charges ~ smoker + age + bmi + children + region, data = df)

anova(mod1, mod2)
```

This tells us that adding `region` as a predictor does not improve our model.

```{r}
mod1 = lm(charges ~ smoker + age + bmi + children, data = df)
mod2 = lm(charges ~ smoker + age + bmi + children + sex, data = df)

anova(mod1, mod2)
```

Similarly, this tells us that including `sex` as a predictor does not improve our model either. Based on our ANOVA  tests, our best model has the formula of `charges ~ smoker + age + bmi + children`. However, to ensure our model is performing well, I will test that model's performance against one with all features included based on metrics such as mean absolute error (MAE) and root mean squared error (RMSE), which are commonly used to evaluate regression models.

```{r}
# here is where i will do ^^^
mod1 = lm(charges ~ smoker + age + bmi + children, data = df)
mod2 = lm(charges ~ smoker + age + bmi + children + region, data = df)
mod3 = lm(charges ~ smoker + age + bmi + children + sex, data = df)
mod4 = lm(charges ~ ., data = df)

model_summaries = data.frame(model = c("anova", "region", "sex", "full"),
           mae = c(MAE(mod1$fitted.values, df$charges),
                   MAE(mod2$fitted.values, df$charges),
                   MAE(mod3$fitted.values, df$charges),
                   MAE(mod4$fitted.values, df$charges)),
           rmse = c(RMSE(mod1$fitted.values, df$charges),
                    RMSE(mod2$fitted.values, df$charges),
                    RMSE(mod3$fitted.values, df$charges),
                    RMSE(mod4$fitted.values, df$charges)),
           rsq = c(summary(mod1)[[8]], summary(mod2)[[8]], summary(mod3)[[8]], summary(mod4)[[8]]),
           adj_rsq = c(summary(mod1)[[9]], summary(mod2)[[9]], summary(mod3)[[9]], summary(mod4)[[9]]))

model_summaries |>
  mutate(mae = round(mae, 4),
         rmse = round(rmse, 4),
         rsq = round(rsq, 4),
         adj_rsq = round(adj_rsq, 4))
```

The rankings (from best to worst) for each of the metrics among the different models are as follows:

`MAE`

1. Full model
2. Region model
3. ANOVA model
4. Sex model

`RMSE`

1. Full model
2. Region model
3. Sex model
4. ANOVA model

`RSQ`

1. ANOVA model
2. Sex model
3. Region model
4. Full model

`ADJ RSQ`

1. Sex model
2. ANOVA model
3. Full model
4. Region Model






























































